---
title: "Step 1: Data management"
subtitle: "Longitudinal association of homonegative school climate with body dysmorphic disorder among cisgender sexual minority adolescents: Testing mediational effects of proximal stressors"
author: "F. Hunter McGuire, MPH"
date: "`r format(Sys.Date(), format='%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: false
    theme: readable
    highlight: zenburn
urlcolor: blue
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: console
---

# Load data and packages

```{r setup, message=FALSE, warning=FALSE}

knitr::opts_chunk$set(warning=FALSE, message=FALSE)

# load packages
library(readxl) # load excel files
library(tidyr) # data management tasks
library(dplyr) # data management tasks
library(mice) # multiple imputation with chained equations

## set working directory to source file location
### get full file path
RMDpath <- rstudioapi::getSourceEditorContext()$path
### remove file name from file path
RMDpath <- gsub('/01_asets_dataManagement.Rmd','', RMDpath)
### set the working directory
setwd(RMDpath)

# load full longitudinal data frame
asets <- read_excel("asets_masterfile.xlsx")

# set variable names to lowercase
names(asets) <- tolower(names(asets))

# limit data frame those who completed at least one wave from 4-6
asets <- asets %>% 
  filter(age_t4!=-99 | age_t5!=-99 | age_t6!=-99)

```

# Pre-imputation data management

## Derive body dysmorphic disorder (BDD) measure

```{r deriveBDD}

asets <- asets %>% 
  # define the 3-level BDD variable
  # 0 = No BDD; 1 = BDD with thin/fat concerns; 2 = BDD with other concerns
  mutate(
  ##########
  # Wave 4 #
  ##########
    bdd_t4 = case_when(
      # No appearance concerns
      bdd_1_t4==0 ~ 0, 
      # appearance concerns, but no impairments
      bdd_1_t4==1 & 
        (bdd_2a_t4==0 & bdd_2b_t4==0 & bdd_2c_t4==0 & bdd_2d_t4==0) ~ 0,
      # appearance concerns, but does not think about them "a lot"
      bdd_1_t4==1 & (bdd_3_t4==0 | bdd_5_t4==1) ~ 0,
      # BDD, thin/fat as primary concern
      bdd_1_t4==1 & 
        (bdd_2a_t4==1 | bdd_2b_t4==1 | bdd_2c_t4==1 | bdd_2d_t4==1) & 
        bdd_3_t4==1 & bdd_4_t4==1 & bdd_5_t4>1 ~ 1,
      #  BDD, other concerns
      bdd_1_t4==1 & 
        (bdd_2a_t4==1 | bdd_2b_t4==1 | bdd_2c_t4==1 | bdd_2d_t4==1) & 
        bdd_3_t4==1 & bdd_4_t4==0 & bdd_5_t4>1 ~ 2), 
  ##########
  # Wave 5 #
  ##########
    bdd_t5 = case_when(
      # No appearance concerns
      bdd_1_t5==0 ~ 0, 
      # appearance concerns, but no impairments
      bdd_1_t5==1 & 
        (bdd_2a_t5==0 & bdd_2b_t5==0 & bdd_2c_t5==0 & bdd_2d_t5==0) ~ 0,
      # appearance concerns, but does not think about them "a lot"
      bdd_1_t5==1 & (bdd_3_t5==0 | bdd_5_t5==1) ~ 0,
      # BDD, thin/fat as primary concern
      bdd_1_t5==1 & 
        (bdd_2a_t5==1 | bdd_2b_t5==1 | bdd_2c_t5==1 | bdd_2d_t5==1) & 
        bdd_3_t5==1 & bdd_4_t5==1 & bdd_5_t5>1 ~ 1, 
      #  BDD, other concerns
      bdd_1_t5==1 & 
        (bdd_2a_t5==1 | bdd_2b_t5==1 | bdd_2c_t5==1 | bdd_2d_t5==1) & 
        bdd_3_t5==1 & bdd_4_t5==0 & bdd_5_t5>1 ~ 2), 
  ##########
  # Wave 6 #
  ##########
    bdd_t6 = case_when(
      # No appearance concerns
      bdd_1_t6==0 ~ 0, 
      # appearance concerns, but no impairments
      bdd_1_t6==1 & 
        (bdd_2a_t6==0 & bdd_2b_t6==0 & bdd_2c_t6==0 & bdd_2d_t6==0) ~ 0,
      # appearance concerns, but does not think about them "a lot"
      bdd_1_t6==1 & (bdd_3_t6==0 | bdd_5_t6==1) ~ 0,
      # BDD, thin/fat as primary concern
      bdd_1_t6==1 & 
        (bdd_2a_t6==1 | bdd_2b_t6==1 | bdd_2c_t6==1 | bdd_2d_t6==1) & 
        bdd_3_t6==1 & bdd_4_t6==1 & bdd_5_t6>1 ~ 1, 
      # BDD, other concerns
      bdd_1_t6==1 & 
        (bdd_2a_t6==1 | bdd_2b_t6==1 | bdd_2c_t6==1 | bdd_2d_t6==1) & 
        bdd_3_t6==1 & bdd_4_t6==0 & bdd_5_t6>1 ~ 2))

```

## Derive sexual minority adolescent stress inventory (SMASI) items

```{r deriveMinorityStress}

asets <- asets %>% 
  # rename SMASI items to enhance readability
  # set missing data (-88, -99) to NA
  mutate(
    # homonegative school climate - past 30 day (wave 4)
    hsc1_t4 = case_when(sd31_t4==0 ~ 0, sd31_t4==1 ~ 1),
    hsc2_t4 = case_when(sd33_t4==0 ~ 0, sd33_t4==1 ~ 1),
    hsc3_t4 = case_when(sd34_t4==0 ~ 0, sd34_t4==1 ~ 1),
    hsc4_t4 = case_when(sd35_t4==0 ~ 0, sd35_t4==1 ~ 1),
    # homonegative school climate - past 30 day (wave 5)
    hsc1_t5 = case_when(sd31_t5==0 ~ 0, sd31_t5==1 ~ 1),
    hsc2_t5 = case_when(sd33_t5==0 ~ 0, sd33_t5==1 ~ 1),
    hsc3_t5 = case_when(sd34_t5==0 ~ 0, sd34_t5==1 ~ 1),
    hsc4_t5 = case_when(sd35_t5==0 ~ 0, sd35_t5==1 ~ 1),
    # homonegative school climate - past 30 day (wave 6)
    hsc1_t6 = case_when(sd31_t6==0 ~ 0, sd31_t6==1 ~ 1),
    hsc2_t6 = case_when(sd33_t6==0 ~ 0, sd33_t6==1 ~ 1),
    hsc3_t6 = case_when(sd34_t6==0 ~ 0, sd34_t6==1 ~ 1),
    hsc4_t6 = case_when(sd35_t6==0 ~ 0, sd35_t6==1 ~ 1),
    # internalized homonegativity - past 30 day (wave 4)
    ih1_t4 = case_when(sd14_t4==0 ~ 0, sd14_t4==1 ~ 1),
    ih2_t4 = case_when(sd15_t4==0 ~ 0, sd15_t4==1 ~ 1),
    ih3_t4 = case_when(sd16_t4==0 ~ 0, sd16_t4==1 ~ 1),
    ih4_t4 = case_when(sd17_t4==0 ~ 0, sd17_t4==1 ~ 1),
    ih5_t4 = case_when(sd18_t4==0 ~ 0, sd18_t4==1 ~ 1),
    ih6_t4 = case_when(sd19_t4==0 ~ 0, sd19_t4==1 ~ 1),
    ih7_t4 = case_when(sd20_t4==0 ~ 0, sd20_t4==1 ~ 1),
    # internalized homonegativity - past 30 day (wave 5)
    ih1_t5 = case_when(sd14_t5==0 ~ 0, sd14_t5==1 ~ 1),
    ih2_t5 = case_when(sd15_t5==0 ~ 0, sd15_t5==1 ~ 1),
    ih3_t5 = case_when(sd16_t5==0 ~ 0, sd16_t5==1 ~ 1),
    ih4_t5 = case_when(sd17_t5==0 ~ 0, sd17_t5==1 ~ 1),
    ih5_t5 = case_when(sd18_t5==0 ~ 0, sd18_t5==1 ~ 1),
    ih6_t5 = case_when(sd19_t5==0 ~ 0, sd19_t5==1 ~ 1),
    ih7_t5 = case_when(sd20_t5==0 ~ 0, sd20_t5==1 ~ 1),
    # internalized homonegativity - past 30 day (wave 6)
    ih1_t6 = case_when(sd14_t6==0 ~ 0, sd14_t6==1 ~ 1),
    ih2_t6 = case_when(sd15_t6==0 ~ 0, sd15_t6==1 ~ 1),
    ih3_t6 = case_when(sd16_t6==0 ~ 0, sd16_t6==1 ~ 1),
    ih4_t6 = case_when(sd17_t6==0 ~ 0, sd17_t6==1 ~ 1),
    ih5_t6 = case_when(sd18_t6==0 ~ 0, sd18_t6==1 ~ 1),
    ih6_t6 = case_when(sd19_t6==0 ~ 0, sd19_t6==1 ~ 1),
    ih7_t6 = case_when(sd20_t6==0 ~ 0, sd20_t6==1 ~ 1),
    # negative expectancies - past 30 day (wave 4)
    ne1_t4 = case_when(sd4_t4==0 ~ 0, sd4_t4==1 ~ 1),
    ne2_t4 = case_when(sd8_t4==0 ~ 0, sd8_t4==1 ~ 1),
    ne3_t4 = case_when(sd9_t4==0 ~ 0, sd9_t4==1 ~ 1),
    # negative expectancies - past 30 day (wave 5)
    ne1_t5 = case_when(sd4_t5==0 ~ 0, sd4_t5==1 ~ 1),
    ne2_t5 = case_when(sd8_t5==0 ~ 0, sd8_t5==1 ~ 1),
    ne3_t5 = case_when(sd9_t5==0 ~ 0, sd9_t5==1 ~ 1),
    # negative expectancies - past 30 day (wave 6)
    ne1_t6 = case_when(sd4_t6==0 ~ 0, sd4_t6==1 ~ 1),
    ne2_t6 = case_when(sd8_t6==0 ~ 0, sd8_t6==1 ~ 1),
    ne3_t6 = case_when(sd9_t6==0 ~ 0, sd9_t6==1 ~ 1)) 

```

## Derive gender identity measure 

```{r deriveGender}

# take information from all 3 waves to re-code gender into:
# 0 = cisgender girls/women
# 1 = cisgender boys/men
# 2 = transgender and gender expansive

asets <- asets %>% 
  mutate(
  ##########
  # Wave 4 #
  ##########
    gender_t4 = case_when(
      gid_t4==0 & sab_t1==0 ~ 0, # cisgender girls
      gid_t4==1 & sab_t1==1 ~ 1, # cisgender boys
      gid_t4==2 | gid_t4==3 | gid_t4==4 | gid_t4==5 | gid_t4==6 ~ 2,
      gid_t4==0 & sab_t1==1 ~ 2, # identify as girl, male sex at birth
      gid_t4==1 & sab_t1==0 ~ 2, # identify as boy, female sex at birth
      gid_t4==-99 ~ -99), # missing data
  ##########
  # Wave 5 #
  ##########
    gender_t5 = case_when(
      gid_t5==0 & sab_t1==0 ~ 0, # cisgender girls
      gid_t5==1 & sab_t1==1 ~ 1, # cisgender boys
      gid_t5==2 | gid_t5==3 | gid_t5==4 | gid_t5==5 | gid_t5==6 ~ 2,
      gid_t5==0 & sab_t1==1 ~ 2, # identify as girl, male sex at birth
      gid_t5==1 & sab_t1==0 ~ 2, # identify as boy, female sex at birth
      gid_t5==-99 ~ -99), # missing data
  ##########
  # Wave 6 #
  ##########
    gender_t6 = case_when(
      gid_t6==0 & sab_t1==0 ~ 0, # cisgender girls
      gid_t6==1 & sab_t1==1 ~ 1, # cisgender boys
      gid_t6==2 | gid_t6==3 | gid_t6==4 | gid_t6==5 | gid_t6==6 ~ 2,
      gid_t6==0 & sab_t1==1 ~ 2, # identify as girl, male sex at birth
      gid_t6==1 & sab_t1==0 ~ 2, # identify as boy, female sex at birth
      gid_t6==-99 ~ -99), # missing data
    gender_allwave = case_when(
      # cisgender girls/women
      gender_t4==0 & gender_t5==0 & gender_t6==0 ~ 0, # cis w, cis w, cis w
      gender_t4==0 & gender_t5==-99 & gender_t6==0 ~ 0, # cis w, NA, cis w
      gender_t4==0 & gender_t5==0 & gender_t6==-99 ~ 0, # cis w, cis w, NA
      gender_t4==0 & gender_t5==-99 & gender_t6==-99 ~ 0, # cis w, NA, NA
      gender_t4==-99 & gender_t5==-99 & gender_t6==0 ~ 0, # NA, NA, cis w
      gender_t4==-99 & gender_t5==0 & gender_t6==-99 ~ 0, # NA, cis w, NA
      gender_t4==-99 & gender_t5==0 & gender_t6==0 ~ 0, # NA, cis m, cis m
      # cisgender boys/men
      gender_t4==1 & gender_t5==1 & gender_t6==1 ~ 1, # cis m, cis m, cis m
      gender_t4==1 & gender_t5==-99 & gender_t6==1 ~ 1, # cis m, NA, cis m
      gender_t4==1 & gender_t5==1 & gender_t6==-99 ~ 1, # cis m, cis m, NA
      gender_t4==1 & gender_t5==-99 & gender_t6==-99 ~ 1, # cis m, NA, NA
      gender_t4==-99 & gender_t5==-99 & gender_t6==1 ~ 1, # NA, NA, cis m
      gender_t4==-99 & gender_t5==1 & gender_t6==-99 ~ 1, # NA, cis m, NA
      gender_t4==-99 & gender_t5==1 & gender_t6==1 ~ 1, # NA, cis m, cis m
      # transgender & gender expansive
      gender_t4==2 | gender_t5==2 | gender_t6==2 ~ 2)) # TGE at any wave

```

## Derive age, urbanicity, and region variables

```{r deriveAgeUrbanRegion}

asets <- asets %>% 
  # recode urban/rural and region variables
  mutate(
    urban = case_when(urban_t1==0 ~ 0, 
                      urban_t1==1 ~ 1),
    region = case_when(
      region_t1==1 ~ 1,
      region_t1==2 ~ 2,
      region_t1==3 ~ 3,
      region_t1==4 ~ 4,
      region_t1==5 ~ 5)) %>% 
  # recode missing age data using complete age data from other waves
  mutate(
  ##########
  # Wave 4 #
  ##########
    age_t4 = case_when(
      age_t4==14 ~ 14,
      age_t4==15 ~ 15,
      age_t4==16 ~ 16,
      age_t4==17 ~ 17,
      age_t4==18 ~ 18,
      age_t4==19 ~ 19,
      age_t4==-99 & age_t5==16 ~ 15,
      age_t4==-99 & age_t5==17 ~ 16,
      age_t4==-99 & age_t5==18 ~ 17,
      age_t4==-99 & age_t5==19 ~ 18,
      age_t4==-99 & age_t6==16 ~ 15,
      age_t4==-99 & age_t6==17 ~ 16,
      age_t4==-99 & age_t6==18 ~ 17,
      age_t4==-99 & age_t6==19 ~ 18,
      age_t4==-99 & age_t6==20 ~ 19),
  ##########
  # Wave 5 #
  ##########
    age_t5 = case_when(
      age_t5==15 ~ 15,
      age_t5==16 ~ 16,
      age_t5==17 ~ 17,
      age_t5==18 ~ 18,
      age_t5==19 ~ 19,
      age_t5==20 ~ 20,
      age_t5==21 ~ 21,
      age_t5==-99 & age_t4==15 ~ 16,
      age_t5==-99 & age_t4==16 ~ 17,
      age_t5==-99 & age_t4==17 ~ 18,
      age_t5==-99 & age_t4==18 ~ 19,
      age_t5==-99 & age_t4==19 ~ 20, 
      age_t5==-99 & age_t6==16 ~ 15,
      age_t5==-99 & age_t6==17 ~ 16,
      age_t5==-99 & age_t6==18 ~ 17,
      age_t5==-99 & age_t6==19 ~ 18,
      age_t5==-99 & age_t6==20 ~ 19),
  ##########
  # Wave 6 #
  ##########
    age_t6 = case_when(
      age_t6==16 ~ 16,
      age_t6==17 ~ 17,
      age_t6==18 ~ 18,
      age_t6==19 ~ 19,
      age_t6==20 ~ 20,
      age_t6==21 ~ 21,
      age_t6==22 ~ 22,
      age_t6==-99 & age_t4==14 ~ 15,
      age_t6==-99 & age_t4==15 ~ 16,
      age_t6==-99 & age_t4==16 ~ 17,
      age_t6==-99 & age_t4==17 ~ 18,
      age_t6==-99 & age_t4==18 ~ 19, 
      age_t6==-99 & age_t4==19 ~ 20,
      age_t6==-99 & age_t5==16 ~ 17,
      age_t6==-99 & age_t5==17 ~ 18,
      age_t6==-99 & age_t5==18 ~ 19,
      age_t6==-99 & age_t5==19 ~ 20,
      age_t6==-99 & age_t5==20 ~ 21))

```

## Create a subset of the overall dataset

```{r asetsSubset}

# use select function to grab needed items for multiple imputation
asetsSubset <- asets %>% 
  dplyr::select(bdd_t4, bdd_t5, bdd_t6, 
                hsc1_t4, hsc2_t4, hsc3_t4, hsc4_t4,
                hsc1_t5, hsc2_t5, hsc3_t5, hsc4_t5,
                hsc1_t6, hsc2_t6, hsc3_t6, hsc4_t6,
                ih1_t4, ih2_t4, ih3_t4, ih4_t4, ih5_t4, ih6_t4, ih7_t4,
                ih1_t5, ih2_t5, ih3_t5, ih4_t5, ih5_t5, ih6_t5, ih7_t5,
                ih1_t6, ih2_t6, ih3_t6, ih4_t6, ih5_t6, ih6_t6, ih7_t6,
                ne1_t4, ne2_t4, ne3_t4, 
                ne1_t5, ne2_t5, ne3_t5,
                ne1_t6, ne2_t6, ne3_t6,
                urban, region,
                race_t4, gender_allwave, sab_t1)

# due to convergence issues, save the age variable as a data frame
# merge back later on after mice imputation
age <- asets %>% 
  select(age_t4, age_t5, age_t6)

regionUrban <- asets %>% 
  select(region, urban)

```

# Multiple imputation with chained equations (mice)

```{r mice, eval=FALSE}

# extract variable names
col_names <- names(asetsSubset)

# reshape into a data frame
impMethod <- as.data.frame(col_names) 

# define imputation method for each variable
impMethod <- impMethod %>% 
  mutate(method = case_when(
    grepl("bdd", col_names) ~ "polyreg", # polytomous regression (multinomial)
    grepl("hsc", col_names) | 
      grepl("ih", col_names) | 
      grepl("ne", col_names) ~ "logreg", # logistic regression (binary)
    col_names=="race_t4" | 
      col_names=="gender_allwave" |
      col_names=="sab_t1" | col_names=="urban" |
      col_names=="region" ~ "" # no missing data
  ))
# save the imputation method list into a vector for use below
impMethodList <- impMethod$method

# convert all variables to factor/categorical format
asetsSubset[,col_names] <- lapply(asetsSubset[,col_names], factor)

# Run mice to generate 10 imputed data sets
miceImputation <- mice(data=asetsSubset, 
                       m=10, # 10 imputations
                       maxit=10, # 10 iterations per imputation
                       seed=828, # random seed for reproducible results
                       method=impMethodList) # vector of imputation methods

# Save mice output
saveRDS(miceImputation, "miceImputation.RDS")

```

# Post-imputation data management

```{r postMiceDataManagement}

# load the imputed dataset
miceImputation <- readRDS(file="miceImputation.RDS")

# Extract all imputed data sets into a single, wide-format data frame
imputed_wide <- complete(miceImputation, action = "long", include=TRUE) %>% 
  select(-c(region))

# merge with urban and region data

# repeat the age variables to match the row length of the "imp" object
# 11 times (10 imputed datasets + 1 original dataset)
age_rbind <- rbind(age, age, age, age, age, 
                   age, age, age, age, age,
                   age)
regionUrban_rbind <- rbind(regionUrban, regionUrban, regionUrban, regionUrban,
                           regionUrban, regionUrban, regionUrban, regionUrban,
                           regionUrban, regionUrban, regionUrban)

# merge age variables back into this dataset
imputed_wide <- cbind(imputed_wide, age_rbind, regionUrban_rbind)

# convert all variables back to numeric format
imputed_wide <- data.frame(lapply(imputed_wide, function(x) 
  as.numeric(as.character(x))))

```

## Derive SMASI subscales, BDD indicators, and race/ethnicity indicators

```{r smasiSubscales}

# dervie SMASI subscale scores
imputed_wide <- imputed_wide %>% 
  # sum scores
  mutate(
    # homonegative school climate
    hsccount_t4 = hsc1_t4+hsc2_t4+hsc3_t4+hsc4_t4,
    hsccount_t5 = hsc1_t5+hsc2_t5+hsc3_t5+hsc4_t5,
    hsccount_t6 = hsc1_t6+hsc2_t6+hsc3_t6+hsc4_t6,
    # internalized homonegativity (wave 4)
    ihcount_t4 = ih1_t4+ih2_t4+ih3_t4+ih4_t4+ih5_t4+ih6_t4+ih7_t4,
    ihcount_t5 = ih1_t5+ih2_t5+ih3_t5+ih4_t5+ih5_t5+ih6_t5+ih7_t5,
    ihcount_t6 = ih1_t6+ih2_t6+ih3_t6+ih4_t6+ih5_t6+ih6_t6+ih7_t6,
    # negative expectancies (wave 4)
    necount_t4 = ne1_t4+ne2_t4+ne3_t4,
    necount_t5 = ne1_t5+ne2_t5+ne3_t5,
    necount_t6 = ne1_t6+ne2_t6+ne3_t6
  ) %>%
  # percentage scores
  mutate (
    hscpct_t4 = (hsccount_t4/4)*10,
    hscpct_t5 = (hsccount_t5/4)*10,
    hscpct_t6 = (hsccount_t6/4)*10,
    ihpct_t4 = (ihcount_t4/7)*10,
    ihpct_t5 = (ihcount_t5/7)*10,
    ihpct_t6 = (ihcount_t6/7)*10,
    nepct_t4 = (necount_t4/3)*10,
    nepct_t5 = (necount_t5/3)*10,
    nepct_t6 = (necount_t6/3)*10
  ) %>% 
  # binary scores
  mutate(
    hscbinary_t4 = ifelse(hsccount_t4>=1, 1, 0),
    hscbinary_t5 = ifelse(hsccount_t5>=1, 1, 0),
    hscbinary_t6 = ifelse(hsccount_t6>=1, 1, 0),
    ihbinary_t4 = ifelse(ihcount_t4>=1, 1, 0),
    ihbinary_t5 = ifelse(ihcount_t5>=1, 1, 0),
    ihbinary_t6 = ifelse(ihcount_t6>=1, 1, 0),
    nebinary_t4 = ifelse(necount_t4>=1, 1, 0),
    nebinary_t5 = ifelse(necount_t5>=1, 1, 0),
    nebinary_t6 = ifelse(necount_t6>=1, 1, 0)
  ) %>% 
  # derive bdd total score (binary) from 3-level score
  mutate(
    # BDD with other concerns only
    bddbin2_t4 = ifelse(bdd_t4==2, 1, 0), 
    bddbin2_t5 = ifelse(bdd_t5==2, 1, 0),
    bddbin2_t6 = ifelse(bdd_t6==2, 1, 0),
    bddbin2_overall = ifelse(bddbin2_t4==1 | bddbin2_t5==1 | 
                               bddbin2_t6==1, 1, 0), # any time point
    bddbinThinFat_t4 = ifelse(bdd_t4==1 | bdd_t4==2, 1, 0),
    bddbinThinFat_t5 = ifelse(bdd_t5==1 | bdd_t5==2, 1, 0),
    bddbinThinFat_t6 = ifelse(bdd_t6==1 | bdd_t6==2, 1, 0),
    bddbinThinFat_overall = ifelse(bddbinThinFat_t4==1 | bddbinThinFat_t5==1 | 
                                     bddbinThinFat_t6==1, 1, 0) # any time point
  ) %>% 
  # white and POC indicator variables
  mutate(
    asian = ifelse(race_t4==2, 1, 0),
    black = ifelse(race_t4==3, 1, 0),
    white = ifelse(race_t4==4, 1, 0),
    hispanic = ifelse(race_t4==5, 1, 0),
    otherMultiracial = ifelse(race_t4==1 | race_t4==6, 1, 0)
  ) %>% 
  # gender indicator variables
  mutate(
    cisgenderGirl = ifelse(gender_allwave==0, 1, 0),
    cisgenderBoy = ifelse(gender_allwave==1, 1, 0),
    transgender = ifelse(gender_allwave==2, 1, 0)) %>% 
  # create new PID variable equal to .id (needed later for pivot_longer)
  mutate(pid = .id)

```

## Pivot from wide to long data format

```{r pivotLonger}

# define function to pivot data from wide to long format
# Source: https://stats.stackexchange.com/questions/515598/is-it-possible-to-imput-values-using-mice-package-reshape-and-perform-gee-in-r
working_dats <- list()
for(i in 0:max(imputed_wide$.imp)) {
  working_dats[[i+1]] <- 
    imputed_wide %>%
    subset(.imp == i) %>%
    dplyr::select(.imp, .id, pid, race_t4, white, asian,
                  black, hispanic, otherMultiracial,
                  gender_allwave, cisgenderGirl, cisgenderBoy, transgender,
                  region, urban, completeall, sab_t1,
                  age_t4, age_t5, age_t6,
                  ihcount_t4, ihcount_t5, ihcount_t6,
                  necount_t4, necount_t5, necount_t6,
                  hsccount_t4, hsccount_t5, hsccount_t6,
                  ihpct_t4, ihpct_t5, ihpct_t6,
                  nepct_t4, nepct_t5, nepct_t6,
                  hscpct_t4, hscpct_t5, hscpct_t6,
                  ihbinary_t4, ihbinary_t5, ihbinary_t6,
                  nebinary_t4, nebinary_t5, nebinary_t6,
                  hscbinary_t4, hscbinary_t5, hscbinary_t6,
                  bddbin2_t4, bddbin2_t5, bddbin2_t6,
                  bddbinThinFat_t4, bddbinThinFat_t5, bddbinThinFat_t6,
                  bddbin2_overall, bddbinThinFat_overall) %>% 
    mutate(pid = .id) %>% 
    pivot_longer(cols = -c(.imp, .id, pid, race_t4, white, asian,
                           black, hispanic, otherMultiracial,
                           gender_allwave, cisgenderGirl, cisgenderBoy,
                           transgender, region, urban, sab_t1, completeall,
                           bddbin2_overall, bddbinThinFat_overall),
               names_sep="_", names_to=c(".value", "grp")) %>%
    mutate(pid = .id,
           .id = 1:nrow(.),
           time = case_when(
             grp=="t4" ~ 0, # baseline
             grp=="t5" ~ 0.5, # 6 months
             grp=="t6" ~ 1 # 12 months
           )) 
}

# save into long format
imputed_long <- do.call(rbind, working_dats)

```

## Generate person mean-centered SMASI variables and grand mean-centered age variable

```{r personMeanCenter}

imputed_long <- imputed_long %>% 
  # generate person-specific means for continuous variables
  group_by(.imp, pid) %>% 
  mutate(
    personMean_hscpct = mean(hscpct, na.rm=TRUE),
    personMean_ihpct = mean(ihpct, na.rm=TRUE),
    personMean_nepct = mean(nepct, na.rm=TRUE),
    personMean_hscbinary = mean(hscbinary, na.rm=TRUE),
    personMean_ihbinary = mean(ihbinary, na.rm=TRUE),
    personMean_nebinary = mean(nebinary, na.rm=TRUE)
  ) %>% 
  ungroup() %>% 
  # generate grand mean age value by imputed dataset
  group_by(.imp) %>% 
  mutate(
    grandMean_age = mean(age, na.rm=TRUE)
  ) %>% 
  ungroup() %>% 
  # create person-centered variables by subtracting out person-specific means
  mutate(
    # continuous predictors
    personMeanCenter_hscpct = hscpct - personMean_hscpct,
    personMeanCenter_ihpct = ihpct - personMean_ihpct,
    personMeanCenter_nepct = nepct - personMean_nepct,
    grandMeanCenter_age = age - grandMean_age,
    # binary predictors
    personMeanCenter_hscbinary = hscbinary - personMean_hscbinary,
    personMeanCenter_ihbinary = ihbinary - personMean_ihbinary,
    personMeanCenter_nebinary = nebinary - personMean_nebinary)
    
```

# Save the final data sets

```{r saveData, eval=FALSE}
# save the dataset in mids (imputed) format
imputed_long <- as.mids(imputed_long)

# cisgender data set
imputed_long_cisgender <- imputed_long %>% 
  filter(gender_allwave<2)

# transgender data set
imputed_long_transgender <- imputed_long %>% 
  filter(gender_allwave==2)

# Save the files!
saveRDS(imputed_long, file="imputed_long.RDS")
saveRDS(imputed_long_cisgender, file="imputed_long_cisgender.RDS")
saveRDS(imputed_long_transgender, file="imputed_long_transgender.RDS")

```

